HFI in RISC-V

### 2025-03-27 paper.tex
finished references

\section{Related Work}
Several alternate approaches have been developed over the years for fine-grained isolation involving hardware-assisted techniques. Some systems have proposed extensions to the page table metadata such as Donky \cite{Donky}, whi
Our work on HFI for RSIC-V builds on prior work that established HFI for x86-64 architectures \cite{HFI}. 
There are also several alternate approaches have been developed over the years for fine-grained isolation involving hardware-assisted techniques. Some systems have proposed extensions to the page table metadata to store a per-sandbox ID checked by hardware, such as Donky \cite{Donky} or IMIX \cite{IMIX}. Donky has been implemented for both x86 and RISC-V architectures, while IMIX has only been implemented on x86. In addition to this, there are also methods that make use of capability-based addressing, a m, which is seen most prominently in Cheri \cite{CHERI}, which has been implemented for RISC-V. While Cheri is a strong security model, it requires extensive modification of the software, and hardware including the OS, ABI, and compiler.

@@

>>>>

\section{Related Work}
Our work on HFI for RSIC-V builds on prior work that established HFI for x86-64 architectures \cite{HFI}. 
There are also several alternate approaches have been developed over the years for fine-grained isolation involving hardware-assisted techniques. Some systems have proposed extensions to the page table metadata to store a per-sandbox ID checked by hardware, such as Donky \cite{Donky} or IMIX \cite{IMIX}. Donky has been implemented for both x86 and RISC-V architectures, while IMIX has only been implemented on x86. In addition to this, there are also methods that make use of capability-based addressing, a scheme for controlling access to memory, which is seen most prominently in Cheri \cite{CHERI}, which has been implemented for RISC-V. While Cheri is a strong security model, it requires extensive modification of the software, and hardware including the OS, ABI, and compiler.

@@

\bibitem{QEMU}
About qemu (no date) About QEMU - QEMU documentation. Available at: https://www.qemu.org/docs/master/about/index.html (Accessed: 26 March 2025).

\bibitem{ResearchGate}
Performance comparison between models and other simulators We evaluated the performance. Retrieved from https://www.researchgate.net/figure/Performance-comparison-between-models-and-other-simulators-We-evaluated-the-performance-fig2-341640101

\bibitem{Opcode}
Anon. Adding a custom instruction in the RVI subset. Retrieved March 26, 2025 from https://pcotret.gitlab.io/riscv-custom/adding-custom.html#custom-opcodes
